Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-08-14 paper/snakemajoranas.tex
finish the appendix part (only Tom's figure is missing

\comment{Short trajectories are less sensitive to the alignment of magnetic field.}

\comment{Zigzag geometry removes the need for precise field alignment.}

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
\caption{A comparison of a straight device (a) and a zigzag one (b) where the magnetic field is rotated.
On the x-axis is the the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
The colormaps and the y-axis have a different scale for both panels.
We see that the device with the zigzag geometry is much more resilient against a misaligned magnetic field.
\label{fig:tilted_angle_phase_diagram}}
\end{figure}

>>>>

\comment{Short trajectories are less sensitive to the alignment of magnetic field.}
Besides short trajectories having a larger $E_\textrm{gap}$, we also find that they are less sensitive to the alignment of the magnetic field.

\comment{Zigzag geometry removes the need for precise field alignment.}
Because the zigzag geometry cuts off long trajectories---leaving only short trajectories---this device will require a less precise alignment of the magnetic field.
To show this, we have performed a simulation of a straight and zigzag device where we rotate the field, and the results are in Fig.~\ref{fig:tilted_angle_phase_diagram}.
We observe that at a $10\circ$ misaligned magnetic field, the zigzag device still has a sizeable gap, wherein the staight device a $1\circ$ misalignment would be detrimental.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/tilted_angle_phase_diagram.pdf}
\caption{A comparison of a straight device (a) and a zigzag one (b) where the magnetic field is rotated.
On the x-axis is the magnetic field $B$ and on the y-axis is the angle $\theta=\arctan{B_y/B_x}$ in degrees.
The colormaps and the y-axis have a different scale for both panels.
We see that the device with the zigzag geometry is much more resilient against a misaligned magnetic field.
\label{fig:tilted_angle_phase_diagram}}
\end{figure}
